Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-11 paper/paper.tex
Add new plots for fig6

Using 0.1 mM KCl solution in HCR, we measured $\xi$ as a function of
$V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
electrochemical reactions (\Fig{} \ref{fig:2}c). We observe an
asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
a higher degree of salt rejection for $V_{\mathrm{G}}>0$. where
positive carriers (holes) are induced in graphene. We notice that an
increase of $\xi$, or a decrease of $\boldsymbol{J}_{\mathrm{PG}}$
with $V_{\mathrm{G}}$, showing an inverse trend compared with those
observed in ionic field effect transistors (IFETs) in which the
diffusive flux increases with the gate voltage
\cite{Nam_2009,Cheng_2018}. A further increase of the KCl
concentration $c_{0}$ influences the attainable degree of salt
rejection. $\xi$ values measured at $V_{\mathrm{G}}$ = 1.25 V,
$\xi_{\mathrm{max}}$, as a function of $c_{0}$ from 10$^{-4}$ to
10$^{-2}$ M KCl (see Supplementary Section \ref{SI-sec:debye}) exhibit a power law
dependency (\Fig{} \ref{fig:2}d). The $\xi_{\mathrm{max}}-c_{0}$
relation can be nicely fitted by a power law function following
$\xi_{\mathrm{max}} c_{0}^{0.59} = \mathrm{constant}$. As the Debye
length in solution, $\lambda_{\mathrm{D}}$, is inversely proportional
to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced salt
rejection originates from the modulation of the electrical double
layer (EDL), as will be discussed later.

>>>>

Using 0.1 mM KCl solution in HCR, we obtained $\xi$ as a function of
$V_{\mathrm{G}}$ within $\pm1.25$ V, before triggering the
electrochemical reactions (\Fig{} \ref{fig:2}c). We observe an
asymmetric dependence of $\xi$ with respect to $V_{\mathrm{G}}$, with
a higher degree of salt rejection for $V_{\mathrm{G}}>0$. where
positive carriers (holes) are induced in graphene. We notice that an
increase of $\xi$, or a decrease of flux through PG with
$V_{\mathrm{G}}$, showing an inverse trend compared with those
observed in ionic field effect transistors (IFETs) in which the
diffusive flux increases with the gate voltage
\cite{Nam_2009,Cheng_2018}. A further increase of the KCl
concentration $c_{0}$ influences the attainable degree of salt
rejection. $\xi$ values measured at $V_{\mathrm{G}}$ = 1.25 V,
$\xi_{\mathrm{max}}$, as a function of $c_{0}$ from 10$^{-4}$ to
10$^{-2}$ M KCl (see Supplementary Section \ref{SI-sec:debye}) exhibit
a power law dependency (\Fig{} \ref{fig:2}d). The
$\xi_{\mathrm{max}}-c_{0}$ relation can be nicely fitted by a power
law function following
$\xi_{\mathrm{max}} c_{0}^{0.52} = \mathrm{constant}$. As the Debye
length in solution, $\lambda_{\mathrm{D}}$, is inversely proportional
to $c^{0.5}$, we infer that the $V_{\mathrm{G}}$-induced salt
rejection originates from the modulation of the electrical double
layer (EDL), as will be discussed later.
